Wissenschaftliches Arbeiten

### 2014-06-29 review-log.tex
Fixing that \{l,r}angle only work in math mode
Adding another sentence to the dummy item description for clarity
Rewriting the conclusion
Answering the comments of the greater outlook and the bit missing depth

\section{Language \& Style}
\subsection{However sometimes either the wording is confusing or I do not get the message right. E.g. ``Another fairness criteria could be that the minimum utility is maximized.'' (1)}
Rephrased and extended.
\subsection{Another point is that it is more common to use cannot instead of `can not' and another instead of `an other'. (1)}
Searched and Replaced.
\subsection{Im Großen und Ganzen in Ordnung. Ein Zeitfehler in Kapitel 3, letzter Absatz: ``From this set they chose that'', hier gehört choose(Gegenwart) (2)}
Corrected typo.
\subsection{In section 4 Bidding Representations \& Languages the article says ``To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundle he or she wants to bid for.'' The word bundle is missing the -s ending for plural. (3)}
Corrected typo.
\subsection{Use of correct/better brackets in section 3 instead of less-than and greater-than signs. (3)}
Replaced all tupel brackets with \langle and \rangle. Also fixed two missing set brackets.
\subsection{On page six the paper says ``During the previous section some small examples were already given but the following ones will go a bit deeper into real work applications.'' I think there is a typo and it should say real world applications. (3)}
Corrected auto correction.

@@

\section{Clarity}
\subsection{In Kapitel 1.2, letzter Satz geht nicht ganz klar hervor was ``ordinal preference'' bedeutet. (2)}
Extended the example a bit.
\subsection{In the restaurant example in section 1.5 Combinatorial Domains it is not clear at first glance that the author does not use a combinatorial voting system. (3)}
Redefined the example a bit by stripping not needed parts and reworked the text in general.
\subsection{In section 4 Bidding Representations \& Languages I think the part about XOR-bids can benefit from some more explanations. I feel that it would be easier to understand, if the the dummy items would have been explained further. [FLBS99] actually has a better example.}
\subsection{On page five the article says ``Its upper limit is $O(n^n)$.'' without saying what n is. (3)}
Added.

@@

\section{Further Suggestions}
\subsection{Table of Contents (2)}
\subsection{Greater outlook (1)}
\subsection{More in-depth (1)}
\subsection{I would have liked it even more if the conclusion had been a bit longer to summarize the whole article once more (and not just in short terms) since I prefer to have a good overview over the things I have already read so that it sticks in my mind better. (1)}

>>>>

\section{Language \& Style}
\subsection{However sometimes either the wording is confusing or I do not get the message right. E.g. ``Another fairness criteria could be that the minimum utility is maximized.'' (1)}
Rephrased and extended.
\subsection{Another point is that it is more common to use cannot instead of `can not' and another instead of `an other'. (1)}
Searched and Replaced.
\subsection{Im Großen und Ganzen in Ordnung. Ein Zeitfehler in Kapitel 3, letzter Absatz: ``From this set they chose that'', hier gehört choose(Gegenwart) (2)}
Corrected typo.
\subsection{In section 4 Bidding Representations \& Languages the article says ``To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundle he or she wants to bid for.'' The word bundle is missing the -s ending for plural. (3)}
Corrected typo.
\subsection{Use of correct/better brackets in section 3 instead of less-than and greater-than signs. (3)}
Replaced all tupel brackets with $\langle$ and $\rangle$. Also fixed two missing set brackets.
\subsection{On page six the paper says ``During the previous section some small examples were already given but the following ones will go a bit deeper into real work applications.'' I think there is a typo and it should say real world applications. (3)}
Corrected auto correction.

@@

\section{Clarity}
\subsection{In Kapitel 1.2, letzter Satz geht nicht ganz klar hervor was ``ordinal preference'' bedeutet. (2)}
Extended the example a bit.
\subsection{In the restaurant example in section 1.5 Combinatorial Domains it is not clear at first glance that the author does not use a combinatorial voting system. (3)}
Redefined the example a bit by stripping not needed parts and reworked the text in general.
\subsection{In section 4 Bidding Representations \& Languages I think the part about XOR-bids can benefit from some more explanations. I feel that it would be easier to understand, if the the dummy items would have been explained further. [FLBS99] actually has a better example.}
Added another sentence for explanation.
\subsection{On page five the article says ``Its upper limit is $O(n^n)$.'' without saying what n is. (3)}
Added.

@@

\section{Further Suggestions}
\subsection{Table of Contents (2)}
I do not think that a table of contents is necessary for such a short paper.
\subsection{Greater outlook (1) \& More in-depth (1)}
I just found some more about current research for the presentation but it also is much more complicated (as described during the presentation).
\subsection{I would have liked it even more if the conclusion had been a bit longer to summarize the whole article once more (and not just in short terms) since I prefer to have a good overview over the things I have already read so that it sticks in my mind better. (1)}
I have extended the closing words.
